### 2015-05-23 docs/report/initialization.tex

\subsection{High start-up time}
This factor raises the issue of when workers should be instantiated. On relation to this, we performed a benchmark to get an idea of the difference between cold starting a worker against having an already available one process messages.

@@

\subsubsection{Conclusion}
The previous benchmark shows a huge difference between the time required to process a message on a pre-existent Web Worker and that necessary to start Web Worker and process a message. For that reason, we decided to create a pool of Web Workers when the library is initialized.

@@

\subsection{Maximum amount of workers}
Since the work being done is CPU intensive (i.e.: the workers' goal is not to perform I/O operations), the maximum amount of workers to be created should not be greater than the amount of cores in the machine \(W_{cores}\), otherwise interleaving would start to affect performance. Additionally, considering the necessity of users to control how many workers are created, an upper bound can be specified \(W_{upper bound}\). If no upper bound is specified, the user upper bound for workers is assumed to be infinite (because the user is not providing a restriction). To summarize, the number of workers to be instantiated is:
\[W = min(W_{cores}, W_{upper bound})\]

>>>>

\subsection{High start-up time}
This factor raises the issue of when workers should be instantiated. On relation to this, we performed a benchmark to get an idea of the difference in time taken to process messages. One scenario considers cold starting a Web Worker, and the other one having a Web Worker already available.

@@

\subsubsection{Conclusion}
The previous benchmark shows a huge difference between the time required to process a message on a pre-existent Web Worker compared to the one necessary to start a Web Worker and process a message. For that reason, we decided to create a pool of Web Workers when the library is initialized and dispatch work to them when it arrives. Since operations are asynchronous, if an operation is executing when another one is added for processing, the latter will be added to a queue and processed when the former completes.

@@

\subsection{Maximum amount of workers}
Since the work being done is CPU intensive (i.e.: the workers' goal is not to perform I/O operations), the maximum amount of workers to be created should not be greater than the amount of cores in the machine \(W_{cores}\), otherwise interleaving would start to affect performance. Additionally, considering the necessity of users to control how many workers are created, an upper bound can be specified \(W_{upper bound}\)\footnote{If the executing browser does not have an API to detect the amount of cores in a device \(W_{cores}=W_{upper bound}\). If no \(W_{upper bound}\) is provided, \(W_{cores}=1\).}. If no upper bound is specified, the user upper bound for workers is assumed to be infinite (because the user is not providing a restriction). To summarize, the number of workers to be instantiated is:
\[W = min(W_{cores}, W_{upper bound})\]

### 2015-05-23 docs/report/inlining.tex

\section{The importance of function inlining}
One of the things found while comparing the performance of the parallel and non-parallel implementations of \code{map} is that our parallel implementation performed a lot worse than what the one expected when considering the size of the \ttarray{} and the \code{mapper} function.

@@

\subsection{The hypothesis}
As the two code samples were similar our hypothesis was that for some reason some v8 optimizations were not taking place. It was a definite possibility considering that the parallel implementation depends on the \tfunction constructor to create \tfunction objects in the Web Workers. Specifically we believed that the internal functions \code{noise}, \code{clamp} and \code{colorDistance} were not being inlined. Inlining could be the cause of both benefits\cite{inline-pro} and drawbacks\cite{inline-cons} but the belief was that performance was being affected because of lack of it

>>>>

\section{The importance of function inlining}
One of the things found while comparing the performance of the parallel and non-parallel implementations of \code{map} is that our parallel implementation performed a lot worse than expected when considering the size of the \ttarray{} and the \code{mapper} function.

@@

\subsection{The hypothesis}
As the two code samples were similar our hypothesis was that for some reason some v8 optimizations were not taking place. It was a definite possibility considering that the parallel implementation depends on the \tfunction{} constructor to create \tfunction{} objects in the Web Workers. Specifically we believed that the internal functions \code{noise}, \code{clamp} and \code{colorDistance} were not being inlined. Inlining could be the cause of both benefits\cite{inline-pro} and drawbacks\cite{inline-cons} but the belief was that performance was being affected because of lack of it
